### 2014-12-11 paper.tex

 \subsection{Redistricting Processes}
Taking in the states with at least 10 congressional districts, using both compactness and vote efficiency as a metric for measuring gerrymandering, we also find that purely legislative processes for redistricting produce more  
  \section{Discussion}
  \subsection{Usefulness of Different Metrics}
  \subsubsection{Compactness Metrics}
  Metrics that use the convex hull of a district are based on the observation that problematic districts are likely to have a section ``cut out'', jut out into a neighboring district, or stretch out in a long, narrow, curved line. Like the perimeter metric, they disadvantage districts with jagged boundaries, although less heavily. The purely geometric version, like other compactness metrics, penalizes states that are non-compact. It particularly affects states that are on a coast and have islands, because a large offshore area gets counted in the convex hull. For example, Californa's 14th district gets an especially bad score because it combines a small, densely populated area with a group of islands several miles offshore. However, the population-based version does not have these issues. In cases where a state has complex boundaries with other states, the population outside of the state can simply be ignored. In cases where a state has islands, the offshore area has no population so it has no effect.
  \subsubsection{Voter Efficiency}
  \subsection{Relationship Between Compactness and Bias Measures}

>>>>

 \subsection{Redistricting Processes}
Taking in the states with at least 10 congressional districts, using both compactness and vote efficiency as a metric for measuring gerrymandering, we also find that purely legislative processes for redistricting produce more gerrymandered districts.   
  \section{Discussion}
  \subsection{Usefulness of Different Metrics}
  \subsubsection{Compactness Metrics}
  Metrics that use the convex hull of a district are based on the observation that problematic districts are likely to have a section ``cut out'', jut out into a neighboring district, or stretch out in a long, narrow, curved line. Like the perimeter metric, they disadvantage districts with jagged boundaries, although less heavily. The purely geometric version, like other compactness metrics, penalizes states that are non-compact. It particularly affects states that are on a coast and have islands, because a large offshore area gets counted in the convex hull. For example, Californa's 14th district gets an especially bad score because it combines a small, densely populated area with a group of islands several miles offshore. However, the population-based version does not have these issues. In cases where a state has complex boundaries with other states, the population outside of the state can simply be ignored. In cases where a state has islands, the offshore area has no population so it has no effect.
  \subsubsection{Voter Efficiency}
  \subsection{Relationship Between Compactness and Bias Measures}
